Fitting Gamma GLMs Multiple Ways

### 2014-04-09 _knitr-posts/2014-04-08-gamma-glms.Rmd
Fix typos

We'll also calculate 95% credible intervals. We'll use HPD intervals ([highest probability denity](http://en.wikipedia.org/wiki/Credible_interval)):

@@

As with many optimization exercises, we can force a term (here `shape`) to be positive by fitting in log-space. Hence, using `logspace` and exponentiating within the optimization function for some of the examples. This creates a smooth likelihood or probability surface near the boundaries that optimization algorithms can better navigate.

>>>>

We'll also calculate 95% credible intervals. We'll use HPD intervals ([highest probability density](http://en.wikipedia.org/wiki/Credible_interval)):

@@

As with many optimization exercises, we can force a term (here `shape`) to be positive by fitting in log-space. Hence, using `logshape` and exponentiating within the optimization function for some of the examples. This creates a smooth likelihood or probability surface near the boundaries that optimization algorithms can better navigate.
